Evolution of precopulatory and postcopulatory inbreeding behaviour

### 2016-09-14 ms_pre_post.Rmd
Add two paragraphs on Discussion: Costs of polyandry and inbreeding avoidance

Our results show that direct negative selection on phenotypes that increase female promiscuity or choosiness with respect to kinship decrease the strength of selection for tendency for polyandry and inbreeding avoidance (Figure 1). Importantly, the cost of tendency for polyandry only decreased female fitness given tendency for polyandry phenotype values greater than zero ($P_{p}>0$), but the threshold nature of the tendency for polyandry phenotype only resulted in selection against positive tendency for polyandry allele values ($P_{a}$) when the sum over a focal female's $20$ $P_{a}$ alleles was greater than zero because summations less than zero all resulted in equivalent monandrous phenotypes ($P_{p}=0$). Hence, even when tendency for polyandry was costly, selection for more negative $P_{a}$ values weakened as the frequency of negative $P_{a}$ values increased and monandry was assured [@Duthie]. This property of threshold traits

>>>>

Our results show that direct negative selection on phenotypes that increase female promiscuity or choosiness with respect to kinship decrease the strength of selection for tendency for polyandry and inbreeding avoidance (Figure 1). Importantly, the cost of tendency for polyandry only decreased female fitness given tendency for polyandry phenotype values greater than zero ($P_{p}>0$), but the threshold nature of the tendency for polyandry phenotype only resulted in selection against positive tendency for polyandry allele values ($P_{a}$) when the sum over a focal female's $20$ $P_{a}$ alleles was greater than zero because summations less than zero all resulted in equivalent monandrous phenotypes ($P_{p}=0$). Hence, even when tendency for polyandry was costly, selection for more negative $P_{a}$ values weakened as the frequency of negative $P_{a}$ values increased because each individual $P_{a}$ then became less influential in causing females to be monandrous [@Duthie]. This general property of threshold traits causes maladaptive phenotypes to frequently reappear within populations due to the mutation and recombination of continuous genetic values underlying discrete phenotypes [@Roff1996; @Roff1998]. Assuming that there is continuous genetic variation underlying threshold polyandry, polyandrous phenotypes are therefore sometimes predicted even when costly [@Duthie], potentially creating the possibility for selection on inbreeding fertilisation strategy when polyandry is expressed. This is most evident in Figure 1C, where mean allele values for polyandry are negative (red line), but strong post-copulatory inbreeding avoidance is still predicted (grey line). Consequently, costly polyandry does not necessarily preclude evolution of adaptive post-copulatory inbreeding avoidance in populations.

A low relative cost for one inbreeding strategy (e.g., pre-copulatory inbreeding avoidance) did not preclude a more costly complementary inbreeding strategy from persisting in a focal population (Figure 1), meaning that evolution of both pre- and post-copulatory inbreeding avoidance might be expected in populations despite cost asymmetry. However, existence of costs strongly affected the evolution of the costly phenotype(s), meaning that quantifying costs is necessary for predicting evolution of phenotypes associated with inbreeding strategies. Quantifying direct costs of phenotypes associated with polyandry and mate choice is empirically challenging [@Pomiankowski1987; @Kokko2003; @Reid2015]. @Pomiankowski1987 categorised four types of costs that are relevant to mate choice, which we suggest are also relevant costs for polyandry, and include costs of elevated risks associated with (1) predation or (2) disease transmission, and costs incurred through loss of time (3) or depletion of energy (4). In our model, we interpreted a cost of tendency for polyandy as an elevated risk of predation as might be incurred while searching for or courting mates [e.g., @Rowe1988; @Rowe1994], a cost of inbreeding mating strategy as a lost of time [i.e., risk of not finding a mate in time due to choosiness; e.g., @Kokko2013], and a cost of inbreeding fertilisation strategy as depletion of energy [e.g., @Tuni2013]. While these costs are biologically realistic, different costs will be relevant for different populations and be realised in different ways. For example, increased risk of disease transmission has been observed for highly polyandrous females [@Roberts2015a], but such a cost would more realistically be applied to the number of realised mates a female has rather than her tendency for engaging in polyandry (as we model). Future models will therefore need to carefully consider the magnitudes and realisation of direct costs to accurately predict evolution of inbreeding strategies in populations.

Another type of cost relevant for polyandry and inbreeding strategy is risk of male harm as a consequence of sexual conflict [e.g., @Arnqvist2005a; @Parker2006]. <!--- Male harm --->
